README for Clayton Stanley's dissertation

### 2014-12-05 docs/README/readme.tex
foo

\documentclass[man,floatsintext,donotrepeattitle]{apa6}
\frenchspacing
\raggedbottom
\title{README for Clayton Stanley's dissertation}
%\shorttitle{Comparing memory models of tag retrieval}
\shorttitle{README}
\author{Clayton Stanley}
\affiliation{Rice University}
\usepackage[group-separator={,}]{siunitx}
\usepackage{csquotes}
\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber,doi=false,uniquename=false]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{bibliography.bib}
%\usepackage{enumitem}
\usepackage{paralist}
\usepackage[doublespacing]{setspace}
\usepackage{tocloft}

@@

>>>>

\documentclass[man,floatsintext,donotrepeattitle]{apa6}
\frenchspacing
\raggedbottom
\title{README for Clayton Stanley's dissertation}
%\shorttitle{Comparing memory models of tag retrieval}
\shorttitle{README}
\author{Clayton Stanley}
\affiliation{Rice University}
\usepackage[group-separator={,}]{siunitx}

\usepackage{csquotes}
\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber,doi=false,uniquename=false]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\usepackage[american]{babel}
\addbibresource{bibliography.bib}

%\usepackage{enumitem}
\usepackage{paralist}
\usepackage[doublespacing]{setspace}
\usepackage{tocloft}

@@

\subsubection{Manual Environment Setup}

Setting up the postgres tables is currently not automated.
This involves creating the tables, all indexes, importing the .csv tables from the source data repository, and then updating the tables with a few additional columns.
This process \emph{was} documented in the form of a script, but that script hasn't been tested.
It contains code for both creating the tables and updating columns in the tables.
Those steps must be done separately, and the tables should be imported into postgres before the updates are called.
Currently that script is located in ``dissProject/createTables.sql''.
I figure that no one other than myself will want to get the database configured,
since the results of all the model runs are saved in separate .csv files and the db is not required to analyze or visualize them.
If I ever have to confiure the database on another machine for this research, I'll separate the ``createTables.sql'' file into two separate files, 
automate and test the whole process, and create an additional make target to configure the db.

\printbibliography[heading=bibintoc]
